---
title: "R Analysis"
author: "Migs Dimayacyac"
date: 2026-09-26
---

``` {r}
#| message: false
#| warning: false
library(tidyverse)
library(palmerpenguins)
```

The data being manipulated in this post is from the Palmer Penguins dataset, loaded in from base R 

(Horst AM, Hill AP, Gorman KB (2020). palmerpenguins: Palmer
Archipelago (Antarctica) penguin data. R package version 0.1.0.
https://allisonhorst.github.io/palmerpenguins/. doi:10.5281/zenodo.3960218.)

``` {r}
penguins_numerical <- penguins |> select(bill_length_mm:body_mass_g) |>  drop_na() |> round()

head(penguins_numerical)
```
Table 1: Palmer Penguins Data Numerical Stats
``` {r}
penguins_grouping <- penguins |> group_by(species, island) |> nest()

head(penguins_grouping)
```
Table 2: Palmer Penguins Grouped by Species and Island
``` {r}
penguins_mass <- penguins |> mutate(body_mass_lb = body_mass_g/453.592) |> select(species, island, body_mass_lb) |> drop_na()

head(penguins_mass)
```
Table 3: Palmer Penguins Mass Grouped By Species and Island